\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
% ****************** 中文 ****************************************
% \usepackage{CJK}
% ****************** 字距包 ****************************************
% \usepackage[final,tracking=smallcaps, expansion=alltext,protrusion=true]{microtype}
% \SetTracking{encoding=*,shape=sc}{50}

% Include information below and uncomment for camera ready
\vldbTitle{A Sample LaTeX Symbols}
\vldbAuthors{}
\vldbDOI{}
\vldbVolume{12}
\vldbNumber{xxx}
\vldbYear{2019}

\begin{document}

% ****************** TITLE ****************************************

\title{A Sample {\ttlit LaTex Symbols}}
\maketitle
% \begin{CJK*}{UTF8}{gkai}

\section{Special Characters}
\# \$ \% \& \textasciitilde \_ \textasciicircum \{  \} \textbackslash

\oe \OE \ae \AE \ss

\'{o} \'{o} \^{o} \~{o} \"{o} \.{o} \v{o} \u{o} \={o} \H{o} \t{oo} \c{o} \d{o} \b{o} \aa \AA \l \L \o \O %?‘ !‘

\mdseries F \normalfont F \rmfamily F \upshape F \itshape F \slshape F \bfseries F \scshape F \sffamily F \ttfamily F

\textmd F \textnormal F \textrm F \textup F \textit F \textsl F \textbf F \textsc F \textsf F \texttt F \normalfont

\qquad - -- \, --- \textemdash \ldots

\section{Special font}

\textbf{Bolder}
Normal text here. 
{% Start a group.
\bfseries
Bold paragraphs in here. 
}% Close the group.
Back to normal text again.

\emph{Emphasis}
Typographic \emph{Style}, or \textbf{Do as he,} %,位置

\textbf{Quotes}
‘Convention’ dictates that punctuation go inside quotes, like ‘‘this,’’ but some think it’s better to do ‘‘this’’.

\textbf{Abb.}
6˜p.m.\ at; Donald˜E. is %缩写写法 

x.; IX\@.%//结尾写法

e.g. i.e. etc. et al.

Fill in the missing word.

Fill in the missing \phantom{word}.

\textbf{Footnotes}
Footnotes\footnote{A footnote is a note of reference, explanation, or comment that is usually placed below the text on a printed page.} can be a nuisance. This is especially true if there are many.\footnote{Like here.} The more you see them, the more annoying they get.\footnote{Got it?}

\textbf{Size}
\tiny a \scriptsize a \footnotesize a \small a \normalsize a \large a \Large a \LARGE a \huge a \Huge a  \begin{small} //use begin-end \end{small}

\normalsize \textsc{No shouting}.

\section{Alignment}
\begin{center}
       Blah.\\ Blah blah blah.
       
       Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah. 
\end{center}

\begin{flushleft} 
       Blah.\\ Blah blah blah.

       Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah. 
\end{flushleft}



% \end{CJK*}
\end{document}
